PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-06-17 paper/ms.tex
minor edits

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{May 15, 2020}
\revised{\today}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{Two Stars, Two Signals, No Planet}

@@

Second, approximately 40-50\% of the transient flux dip stars
discovered in $\rho$~Oph and Upper~Sco show two Lomb-Scargle periods,
\replaced{and so are apparently}{a possible sign of binarity} \removed{binaries}
\citep[][Table~1]{stauffer_orbiting_2017}.  This is higher than the
main-sequence companion fraction of ${\rm
CF}_{0.1\text{-}0.5\,M_\odot}^{\rm MS} = 33 \pm 5\%$\added{, which
could be an indication that the transient flux dip phenomenon is
linked to stellar binarity}
\citep{henry_solar_2006,duchene_stellar_2013,winters_solar_2019}.
\added{This fraction might be even more significant given the
selection bias against high mass ratio binaries, in which the second
star would be too faint to detect a second period.}

@@

\explain{NOTE: This paragraph is newly added, to support our view of the
high-latitude accretion hotspot being plausible for \ptfo.}
The high-latitude accretion hotspot scenario seems 
capable of explaining most of the qualitative characteristics of \ptfo.
Some degree of accretion onto the star seems likely, given 
the H$\alpha$ equivalent width of 11.4$\,$\AA\
\citep{van_eyken_ptf_2012}, which is near the boundary separating ``classical'' and ''weak-lined'' T
Tauri stars \citep{briceno_cidaII_2019}, and the high-velocity
components of the observed H$\alpha$ line profile ($\pm\,200$\,km$\,$s$^{-1}$ \citep{johnskrull_h_2016}.
The non-detection of any NIR excess could be problematic, but does not eliminate the
possibility that a tenuous amount of dust and gas remains near the
star, and is able to accrete onto it.  We view the main problem with
this explanation seems to require rare circumstances,
making it unlikely to be correct for the entire population
of transient flux dips.  RIK-210 in particular has dips that seem too deep
($\sim$20\%) and too asymmetric to be explained by occultations of a
hot spot \citep{david_transient_2017}.

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{May 15, 2020}
\revised{June 16, 2020}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{Two Stars, Two Signals, No Planet}

@@

Second, approximately 40-50\% of the transient flux dip stars
discovered in $\rho$~Oph and Upper~Sco show two Lomb-Scargle periods,
\replaced{and so are apparently binaries}{a possible sign of binarity}
\citep[][Table~1]{stauffer_orbiting_2017}.  This is higher than the
main-sequence companion fraction of ${\rm
CF}_{0.1\text{-}0.5\,M_\odot}^{\rm MS} = 33 \pm 5\%$\added{, which
could be an indication that the transient flux dip phenomenon is
linked to stellar binarity}
\citep{henry_solar_2006,duchene_stellar_2013,winters_solar_2019}.
\added{This fraction might be even more significant given the
selection bias against high mass ratio binaries, in which the second
star would be too faint to detect a second period.}

@@

\explain{NOTE: This paragraph is newly added, to support our view of the
high-latitude accretion hotspot being plausible for \ptfo.}
The high-latitude accretion hotspot scenario seems capable of
explaining most of the qualitative characteristics of \ptfo.  Some
degree of accretion onto the star seems likely, given 
the high-velocity ($\pm\,200$\,km$\,$s$^{-1}$) components of
the observed H$\alpha$ line profile
\citep{johnskrull_h_2016},
as well as the H$\alpha$
equivalent width of 11.4$\,$\AA\ \citep{van_eyken_ptf_2012}, which is
near the boundary separating ``classical'' and ''weak-lined'' T Tauri
stars \citep{briceno_cidaII_2019}.  The non-detection of any NIR excess could
be problematic, but does not eliminate the possibility that a tenuous
amount of dust and gas remains near the star, and is able to accrete
onto it.  The main problem with this explanation is that it seems to
require rare circumstances, making it unlikely to be correct for the
entire population of transient flux dips.  RIK-210 in particular has
dips that seem too deep ($\sim$20\%) and too asymmetric to be
explained by an accretion hot spot \citep{david_transient_2017}.
